Modeling Bandwagoning and Hype in the MLB

### 2020-08-22 Paper_Outline.Rmd
Added another graph

fig1_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_classic() +
  labs(main="Google Trend of Dodgers and Giants", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("dodgerblue", "darkorange"))
```

@@

fig2a_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_classic() +
  labs(main="Google Trend of Dodgers and Giants", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("dodgerblue", "darkorange"))
```

@@

fig2b_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_classic() +
  labs(main="Google Trend of Dodgers and Cubs", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("firebrick2", "dodgerblue"))
```

@@

>>>>

fig1_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_minimal() +
  labs(title="Google Trend of Dodgers and Giants", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("dodgerblue", "darkorange"))
```

@@

fig2a_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_minimal() +
  labs(title="Google Trend of Dodgers and Giants", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("dodgerblue", "darkorange"))
```

@@

fig2b_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_minimal() +
  labs(title="Google Trend of Dodgers and Cubs", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("firebrick2", "dodgerblue"))
```

@@

```{r}
fig3_dat <- read.csv("combined_data.csv")

fig3_dat %>%
  ggplot(aes(x = googlehits)) + 
  geom_histogram(bins = 30,
                 col = "dodgerblue4",
                 fill = "dodgerblue",
                 alpha = 0.7) +
  theme_minimal() + 
  theme(axis.title.y=element_blank()) + 
  labs(main = "Google Trend Hits", x = "Google Hits")

```

```{r}
fig3_dat %>%
  ggplot(aes(x = log(googlehits))) + 
  geom_histogram(bins = 10,
                 col = "dodgerblue4",
                 fill = "dodgerblue",
                 alpha = 0.7) +
  theme_minimal() + 
  theme(axis.title.y=element_blank()) + 
  labs(main = "Google Trend Hits", x = "Google Hits")
```
